Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
some changes to the intro

In this work, we propose the synthesis of \emph{safe} control algorithms for
LTI models taking into consideration the continuous domain of the plant, 
alongside the discrete domain of the controller, 
as well as the hybrid elements that relate them.  
%% In this paper, we synthesize controllers for hybrid
%% closed-loop systems, i.e., software-implemented embedded controllers along
%% with a model of their physical environment (the plant), that are
%% \emph{safe}.
Due to the complexity of such systems, in this work we focus 
on linear models with known  implementation features (e.g., number of bits, fixed-point
arithmetic), %\addtodo{[clarify next] with known configurations} 
and perform %parametric 
synthesis of safe digital controllers -- the extension to more general
quantitative properties is left to future work.

We describe and evaluate two approaches for synthesising digital controllers
for state-space physical plants.  Both approaches consider a counterexample
guided inductive synthesis (CEGIS) loop.  In the first approach, we devise a
digital controller that stabilizes the system whilst remaining safe given a
pre-selected time horizon; then, we verify its potential safety by unfolding
the dynamics of the system and checking for a completeness threshold.  In
the second approach, we substitute the second step by employing abstract
acceleration to unfold the dynamics forward, instead of symbolically
unwinding the transition relation~\cite{cattaruzza2015unbounded}.
\todo{We need to emphasise the derivation of errors for soundness. Can we claim completeness already?}
We provide experimental results 
showing that both approaches are able to efficiently synthesise stable and safe controllers 
for a set of intricate physical plant models taken from the digital 
control literature: the median runtime for our benchmark
set is \textcolor{red}{$XXX$}s, i.e., most controllers can be synthesized in less
than \textcolor{red}{$XXX$} seconds.

@@

%% The safety check is performed in this approach 
%% via unfolding of the transition system corresponding to the synthesized controller
%% up to a completeness threshold. Due to its 
%\todo{mention issue of completeness threshold here?}

>>>>

In this work, we propose the synthesis of \emph{safe} control algorithms for
LTI models taking into consideration the continuous domain of the plant, 
alongside the discrete domain of the controller, 
as well as the hybrid elements that relate them.  
%% In this paper, we synthesize controllers for hybrid
%% closed-loop systems, i.e., software-implemented embedded controllers along
%% with a model of their physical environment (the plant), that are
%% \emph{safe}.
Due to the complexity of such systems, in this work we focus 
on linear models with known  implementation features (e.g., number of bits, fixed-point
arithmetic), and perform 
synthesis of safe digital controllers -- the extension to more general
quantitative properties is left to future work.

We describe and evaluate two approaches for synthesising digital controllers
for state-space physical plants, both based on a counterexample
guided inductive synthesis (CEGIS)~\cite{sketch} loop.
The first approach uses a naive
technique that starts by devising a digital controller that stabilizes the system
whilst remaining safe for a 
pre-selected time horizon and, subsequently, verifies its potential safety by unfolding
the dynamics of the system and checking for a completeness threshold.
As it requires explicit unfolding up to a completeness
threshold, this approach may result in a state space explosion.
Instead of explicitly unfolding the dynamics, the second approach 
employs abstract acceleration~\cite{cattaruzza2015unbounded} to implicitly
evaluate all possible progressions of the system simultaneously.
Additionally, the second approach uses
abstraction refinement enabling us to always start with a very simple description
regardless of the complexity of the overall dynamics, and only expand to more
complex models when a solution cannot be found.

%% we substitute the second step by employing abstract
%% acceleration to unfold the dynamics forward, instead of symbolically
%% unwinding the transition relation~\cite{cattaruzza2015unbounded}.
\todo{We need to emphasise the derivation of errors for soundness. Can we claim completeness already?}

We provide experimental results 
showing that both approaches are able to efficiently synthesise stable and safe controllers 
for a set of intricate physical plant models taken from the digital 
control literature: the median runtime for our benchmark
set is \textcolor{red}{$XXX$}s, i.e., most controllers can be synthesized in less
than \textcolor{red}{$XXX$} seconds.

@@
